---
title: "Lab 10"
author: "Jacika Patel"
date: "6/17/2021"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(rvest)
library(dplyr)
library(tidyverse)
library(repurrrsive)
listviewer::jsonedit(gh_users)  
```

# 1 a) Explain or describe nested Lists.

Nested lists are lists that occurs as an element of another list. Basically, they lists withing a list. They are matrices, it maybe list of rows, where each row is itself a list, or a list of columns where each column is itself a list  
 

# 1 b) Open and explore data for Git Hub repos by running the following code gh_repo. Comment on the structure and arrangement of the data 


When running gh_repos, reading data provided is very confusing. The structure and breakdown makes it hard to navigate the data. 


# 1 c) In two or three sentences, explain what happens to the data when you run the code:
```{r}
repos <- tibble(repo = gh_repos)
repos
```

It shows a nested list that includes 6 repos. From the looking at provided data there 5 repos with 30 lists and 1 with a list of 26. 


# 1 d) Describe the data representation when the listserver tool is applied. And go into detail explaining why we have a nested List configuration. What do the numbers 30 and 68 represent?

```{r}
listviewer::jsonedit(gh_repos)
```

The code above shows the list data for each gh_repo in much simpler way. Using shiny, jsonedit provides a flexible and helpful interactive tree-like view of lists. The gh_repos list  contains another list of 30 user’s repositories. Each of the list of 30 contains 68 element list which contains more information such as; id, name, full_name, owner, and private.


#1 e)  Use and show R unesting code to produce the tibble below.
```{r}
tibble(repo = gh_repos)%>%
  unnest_auto(repo) %>%
  unnest_auto(repo) -> new
new
```
